Global patterns of forest autotrophic carbon fluxes

### 2020-02-07 manuscript/manuscript draft.Rmd
update

We found no evidence that allocation between fluxes varied substantially with latitude or climate. There were no significant results from regressing ratios of carbon fluxes against latitude, or against any of the climate variables.

>>>>

*We found no evidence that allocation between fluxes varied substantially with latitude or climate. There were no significant results from regressing ratios of carbon fluxes against latitude, or against any of the climate variables.* **THIS HAS CHANGED: [issue #51](https://github.com/forc-db/Global_Productivity/issues/51#issuecomment-581892186)
